Expectations, Outcomes, and Challenges \\ of Modern Code Review

### 2013-01-10 sections/limitations.tex
fixed first problem

One common notion is that empirical research within one company or one project provides little value for the academic community, and does not contribute to scientific development. Historical evidence shows otherwise. Flyvbjerg provides several examples of individual cases that contributed to discovery in physics, economics, and social science~\cite{flyvbjerg2006five}. Beveridge observed for social sciences: \quotation{More discoveries have arisen from intense observation than from statistics applied to large groups} (as quoted in Kuper and Kuper~\cite{kuper1995social}, page 95). This should not be interpreted as a criticism of research that focuses on large samples. For the development of an empirical body of knowledge as championed by Basili~\cite{basili1999building}, both types of research are essential. To understand code review across many contexts, we observed, interviewed, surveyed, and examined code reviews from developers across a diverse group of software teams that work with codebases in various domains, of varying sizes, and with varying processes.

>>>>

One potential criticism is that empirical research within one company or one project provides little value for the academic community, and does not contribute to scientific development. Historical evidence shows otherwise. Flyvbjerg provides several examples of individual cases that contributed to discovery in physics, economics, and social science~\cite{flyvbjerg2006five}. Beveridge observed for social sciences: \quotation{More discoveries have arisen from intense observation than from statistics applied to large groups} (as quoted in Kuper and Kuper~\cite{kuper1995social}, page 95). This should not be interpreted as a criticism of research that focuses on large samples. For the development of an empirical body of knowledge as championed by Basili~\cite{basili1999building}, both types of research are essential. To understand code review across many contexts, we observed, interviewed, surveyed, and examined code reviews from developers across a diverse group of software teams that work with codebases in various domains, of varying sizes, and with varying processes.
